Kindly Bent to Free Us

### 2019-07-06 kindly/intro.tex
aff fixed

As a first, well-trodden example we consider a very simple API for
writing files in \cref{fig:writing-files-api}.
The type \lstinline/File.t/ is linear. A call like
\lstinline/fopen "foo"/ returns a linear handle to a newly created
file, which \emph{must} be closed later using
\lstinline/close/. Failing to do so is a static type error.
To write to the file, we must take (mutable) borrows of the handle and
pass them to the \lstinline/write/
function. \Cref{fig:writing-files-example} contains an example where
\lstinline/&!h/ stands for the mutable borrow.

>>>>

As a first, well-trodden example we consider a very simple API for
writing files in \cref{fig:writing-files-api}.
The type \lstinline/File.t/ is linear. A call like
\lstinline/fopen "foo"/ returns a linear handle to a newly created
file, which \emph{must} be closed later using
\lstinline/close/. Failing to do so is a static type error.
To write to the file, we must take a (mutable) borrow of the handle and
pass it to the \lstinline/write/
function. As mutable borrows must not be duplicated so they are
classified as affine. This affinity shows up in the annotation of the
second arrow in the type of \lstinline/write/: a partial application
\lstinline/write &!h/ captures the affine borrow and hence the
resulting function must also be handled in an affine way.
\Cref{fig:writing-files-example} contains an example where
\lstinline/&!h/ stands for the mutable borrow.

This example demostrates two features of our system.
\begin{enumerate}
\item full type inference without annotations in user code
\item types carry multiplicity annotations in the form of kinds
\end{enumerate}

More features: kinds can be polymorphic and constrained.
